---
title: "Example of data generation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example of data generation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this vignette, we will show how to generate realistic datasets. For this example, the data will be simulated based on the `powerconsumption` dataset provides in the package.

```{r setup}
# Load the packages
library(simulater)
```

First, we need to estimate the mean, covariance and noise of the real dataset.
Pay attention that these functions may take some time to execute.

```{r mean, cache=TRUE}
mu <- learn_mean(powerconsumption)
```

```{r cov, cache=TRUE}
cov <- learn_covariance(powerconsumption)
```

```{r noise, cache=TRUE}
noise <- learn_noise(powerconsumption)
```

Then, we can generate some curves using the previous estimated parameters. 

```{r data}
X <- generate_data(10, 100, mu, cov, noise, exp(-5.5), 0.2)
```

```{r plot, echo=FALSE, fig.height=4.35, fig.width=7}
plot(X[[1]]$t, X[[1]]$x, type = 'l', ylim = c(230, 250))
for(i in 2:9){
  lines(X[[i]]$t, X[[i]]$x, col = i)
}
```


```{r data_new}
X <- generate_data(1, 1440, mu, cov, noise, exp(-5.5), 0.2)
```


```{r plot_comp, echo=FALSE, fig.height=4.35, fig.width=7}
plot(X[[1]]$t, X[[1]]$x, type = 'l', col = 'red', ylim = c(230, 250))
lines(seq(0, 1, length.out = 1440), matrix(powerconsumption[1,]), col = 'blue')
```

